\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{A Radial Time Projection Chamber for $\alpha$ detection in CLAS at JLab}

### 2017-02-13 eg6-letters/NIM/EG6_RTPC_NIM.tex
add noise description

The CEBAF Large Acceptance Spectrometer (CLAS)~\cite{CLASref} is installed in 
the Hall-B of the Thomas Jefferson National Accelerator Facility (TJNAF), 
Newport News, Virginia, USA. The accelerator of TJNAF provides, simultaneously, 
a high power electron beam of energy up to 6 GeV and 100$\%$ duty cycle to 
three experimental Halls (A, B, C). The CLAS spectrometer, located in Hall-B, 
is composed of several sub-detectors and two magnets. The spectrometer was 
designed to track charged particles of momentum greater than 250 MeV/c as well 
as detecting real photons. Figure~\ref{fig:CLAS} shows a three dimensional 
representation of the baseline CLAS spectrometer, here is a list of the main elements
depicted in the figure:
\begin{itemize}
 \item The three regions of Drift Chambers (DC) used for the tracking of charged 
    particles~\cite{DCref} (in blue on the figure).
 \item The superconducting toroidal magnet (in yellow) bends the trajectories 
    of charged particles, thus allowing momentum measurement with the DC tracking information.
 \item The Cherenvkov Counters (CC) used to separate electrons from other negative 
    particles, such as pions, at lower energies~\cite{CCref} (in pink).
 \item The Scintillation Counters (SC) used to identify hadrons by measuring their 
    Time-Of-Flight (TOF)~\cite{TOFref} (in red).
 \item The Electromagnetic Calorimeter (EC) used to separate electrons from other negative 
    particles at higher energies and to detect neutral particles (neutrons and 
    photons in particular)~\cite{ECref} (in green).
\end{itemize}

@@

   \item For these selected hits, we look at $\Delta\phi$ ($\Delta \phi$ = 
      $\phi_{sim.}$ - $\phi_{hit\_pad}$) versus TDC. We clearly obtain a 
      correlation shown in figure~\ref{fig:1st_pass_delta_phi}. This $\Delta 
      \phi$ change with TDC shows the drift in $phi$ of the electrons due to 
      the Lorentz angle.

@@

\subsection{Noise Rejection}
Two different characteristic noise signatures were identified and removed during track reconstruction.

The first was an oscillatory noise located early in the readout time window in many channels, shown in the top panel of Figure~\ref{fig:noise}.  The amplitude of the noise is not dissimilar to those of real tracks.  About N\% of the channels exhibit this noise signature.  Due to its unique time-energy correlation for a given channel, the noise could be removed on an event by event and channel by channel basis, without any loss of good signals and the result is illustrated in the bottom panel of Figure~\ref{fig:noise}.

>>>>

The CEBAF Large Acceptance Spectrometer (CLAS)~\cite{CLASref} is installed in 
the Hall-B of the Thomas Jefferson National Accelerator Facility (TJNAF), 
Newport News, Virginia, USA. The accelerator of TJNAF provides, simultaneously, 
a high power electron beam of energy up to 6 GeV and 100$\%$ duty cycle to 
three experimental Halls (A, B, C). The CLAS spectrometer, located in Hall-B, 
is composed of several sub-detectors and two magnets. The spectrometer was 
designed to track charged particles of momentum greater than 250 MeV/c as well 
as detecting real photons. Figure~\ref{fig:CLAS} shows a three dimensional 
representation of the baseline CLAS spectrometer:
\begin{itemize}
 \item The three regions of Drift Chambers (DC) used for the tracking of charged 
    particles~\cite{DCref} (in blue on the figure).
 \item The superconducting toroidal magnet (in yellow) bends the trajectories 
    of charged particles, thus allowing momentum measurement with the DC tracking information.
 \item The Cherenvkov Counters (CC) used to separate electrons from other negative 
    particles, such as pions, at lower energies~\cite{CCref} (in pink).
 \item The Scintillation Counters (SC) used to identify hadrons by measuring their 
    Time-Of-Flight (TOF)~\cite{TOFref} (in red).
 \item The Electromagnetic Calorimeter (EC) used to separate electrons from other negative 
    particles at higher energies and to detect neutral particles (neutrons and 
    photons in particular)~\cite{ECref} (in green).
\end{itemize}

@@

   \item For these selected hits, we look at $\Delta\phi$ ($\Delta \phi$ = 
      $\phi_{sim.}$ - $\phi_{hit\_pad}$) versus TDC. We clearly obtain a 
      correlation shown in figure~\ref{fig:1st_pass_delta_phi}. This $\Delta 
      \phi$ change with TDC shows the azimuthal drift of the electrons due to 
      the Lorentz angle.

@@

\subsection{Noise Rejection}
Two different noise signatures were identified in the raw data and removed in software prior to track reconstruction.

The first is a transient oscillatory noise located early in the readout time window, shown in the top panel of Figure~\ref{fig:noise} for a particularly noisy channel.  Its amplitude is not dissimilar to those of real tracks, and about 18\% of the readout channels exhibit large contributions from this noise characteristic.  Due to its unique time-energy correlation for the given channels, the noise could be removed on an event by event and channel by channel basis without significant loss of good signals, and the result is illustrated in the bottom panel of Figure~\ref{fig:noise}.

The second is a coherent noise affecting about 25\% of the pramplifiers, where the signature is simultaneous hits in most of the 16 channels in a preamp group.  This noise signature is also transient.  An event-based technique to identify and remove it was developed based on counting simultaneous hits in preamp group, and, if sufficiently large, perform a dynamic pedestal subtraction based on the average ADC of the channels' neighbors within the preamp group.

The source of these noises was not determined, but rejection techniques allowed to reconstruct 10\% more good tracks and recover 70 channels that were previously ignored due to high noise levels.
